A state of the art end-to-end speech recognition algorithm with a homogenous structure.

### 2019-09-14 nips_2018_neural_front_end/doc/main.tex
update the papers

%\begin{figure}
%    \centering
%    \resizebox{80mm}{!}{%
%         \input{../figures/entire_diagram.tex}} %
%    \caption {
%      The structure of feature enhancement using peak
%      value normalization and LSTMs.
%      \label{fig:entire_diagam}
%    }
%    %\end{center}
%\end{figure}

@@

\subsection{Simulated utterance generation}
We use the room simulation system introduced in
\cite{C_Kim_INTERSPEECH_2017_1} to generate noisy speech
from clean speech.
\begin{align}
  y[n]
\end{align}
For 
\subsection{Review of the Room Simulator for Data Augmentation}
%
%
%\begin{figure}
%  \centering
%    \begin{subfigure}{\linewidth}
%      \centering
%      \includegraphics[width=70mm]{room_diagram.eps}
%      \caption{}
%      \label{fig:room_diagram}
%    \end{subfigure}
%   \\
%    \begin{subfigure}{\linewidth}
%      \centering
%      \includegraphics[width=70mm]{image_method.eps}
%      \caption{}
%      \label{fig:image_method}
%    \end{subfigure}
%    \caption{
%    (a) A simulated room: There may be multiple microphones, a single target
%    sound source, multiple noise sources in a cuboid-shape room with
%    acoustically reflective walls. (b) A diagram showing the location
%    of the real and the virtual sound sources assuming that the walls
%    reflects acoustic wave like a mirror \cite{C_Kim_INTERSPEECH_2017_1}.}
%  \vspace{-10mm}
%\end{figure}
%
%
In this section, we briefly review the structure of the Google
Room Simulator for generating simulated utterances
to train acoustic models for speech recognition systems
\cite{C_Kim_INTERSPEECH_2017_1}. We assume a room of a
rectangular cuboid-shape as shown in Fig. \ref{fig:room_diagram}.
Assuming that all the walls of a room reflect acoustically uniformly,
we use the image method to model the Room Impulse Responses (RIRs)
\cite{J_Allen_JASA_1979, E_A_Lehmann_ASPAA_2007, S_G_McGovern_RIR}.

>>>>

\begin{figure}
    \centering
    \resizebox{80mm}{!}{%
         \input{../figures/entire_diagram.tex}} %
    \caption {
      The structure of feature enhancement using peak
      value normalization and LSTMs.
      \label{fig:entire_diagam}
    }
    %\end{center}
\end{figure}

@@

\subsection{Simulated utterance generation}
We use the room simulation system introduced in
\cite{C_Kim_INTERSPEECH_2017_1} to generate noisy speech
from clean speech.
\begin{align}
  y[n]
\end{align}
For 
\subsection{Review of the Room Simulator for Data Augmentation}
%
%
\begin{figure}
  \centering
    \begin{subfigure}{\linewidth}
      \centering
      \includegraphics[width=70mm]{room_diagram.eps}
      \caption{}
      \label{fig:room_diagram}
    \end{subfigure}
   \\
    \begin{subfigure}{\linewidth}
      \centering
      \includegraphics[width=70mm]{image_method.eps}
      \caption{}
      \label{fig:image_method}
    \end{subfigure}
    \caption{
    (a) A simulated room: There may be multiple microphones, a single target
    sound source, multiple noise sources in a cuboid-shape room with
    acoustically reflective walls. (b) A diagram showing the location
    of the real and the virtual sound sources assuming that the walls
    reflects acoustic wave like a mirror \cite{C_Kim_INTERSPEECH_2017_1}.}
  \vspace{-10mm}
\end{figure}
%
%
In this section, we briefly review the structure of the Google
Room Simulator for generating simulated utterances
to train acoustic models for speech recognition systems
\cite{C_Kim_INTERSPEECH_2017_1}. We assume a room of a
rectangular cuboid-shape as shown in Fig. \ref{fig:room_diagram}.
Assuming that all the walls of a room reflect acoustically uniformly,
we use the image method to model the Room Impulse Responses (RIRs)
\cite{J_Allen_JASA_1979, E_A_Lehmann_ASPAA_2007, S_G_McGovern_RIR}.

### 2019-09-14 none_feature_mapping_weve/doc/main.tex
update the papers

\begin{abstract}
This paper presents a new robust neural frontend layer referred to as Power
Normalized Neural Frontend (PNNF) for robust speech recognition. PNNF
is implemented as a layer in an end-to-end all neural-network speech 
recognition system. For speech recognition, features such as Mel Filterbank
Cepstral Coefficient (MFCC) or log-Mel have been used very widely.
More recently, features motivated by human auditory processing have shown
improvement under certain conditions. Nevertheless, these auditory
features are constructed using signal processing blocks with hand-crafted
parameters for certain conditions. Therefore, the performance is not
always optimal for various kind of acoustic conditions.
 PNNF frontend layer is loosely motivated by human auditory system.
This processing uses the concept of the auditory masking and the auditory nonlinearity.
However, instead of directly using theories and parameters about human auditory masking,
neural networks make decision about it from the training data.
Even though the structure of the PNNF layer is very simple, this layer
significantly boosts the performance of the speech recognition system.
\end{abstract}

@@

In the feature enhancement process, we estimate a clean feature 
$\vec{y}$ given a corrupt feature $\vec{x}$.

@@

\section{Structure of the neural front-end}

\subsection{Neural nonlinearity}
In this section, we describe our neural nonlinearity algorithm. 
\begin{align}
  \vec{q[m, l]} = \vec{x[m, l]} ^ {\vec{\alpha}} 
\end{align}

\subsection{Neural background removal}
In this section, we describe our Neural Background Removal (NBR) approach.
Fig. \label{fig:nbr_diagram} shows the structure of the NBR processing.

$\vec{q}$ is the non-linearity output defined in

\begin{figure}
    \centering
    \resizebox{80mm}{!}{%
         \input{../figures/background_removal.tex}} %
    \caption {
      The structure of the Neural Background Removal (NBR) block.
      \label{fig:nbr_diagam}
    }
    %\end{center}
\end{figure}

\subsection{  }

>>>>

\begin{abstract}
TODO(chanw.com) Revise the abstract.
This paper presents a new enhacement algorithm using neural networks 
refered to as WEVE (Weighted Enhancement Using Variance Estimation).
The conventional way of feature enhacement is to directly estimate the clean
feature from the corrupt feature. This mapping from the corrupt feature
to the corresponding clean feature is learned using a training database
consisting of a large number of such pairs of corrupt and clean features
usually with the Mean Squared Error (MSE) loss. The problem of such 
conventional techniques is that they do consider the reliablity of enhancement.
We have frequently observed that this enhancement mapping actually degrades
performance rather than enhacing the classification or recognition
performance under certain conditions.  In WEVE, we estimate both the enhanced 
feature and the variance of this estimation. The final output of the enhancement 
block is a linear combination of the original feature and the 
enhanced feature. The weighting is given by the Minimum Mean
Sqaured Error (MMSE) criterion. This process is very simple nontheless
shows significant improvements in our experiments.
\end{abstract}

@@

In the feature enhancement process, we estimate a clean feature 
$\vec{y}$ given a corrupt feature $\vec{x}$. Suppose that
we have

@@

### 2019-09-14 none_feedback_sequence_classifier/doc/main.tex
update the papers

  \Require {$\vec{x}[0:M]$}
  \Require {$\vec{y}_{0:L}$}
  \Require {The beam size $N_b$}
  \Require {The neural network parameter $\Theta^{\left(i\right)}$ 
    for calculating $\vec{z}[u] = f(\vec{x}[0:m+1],\,z[0:u])$}

  \State {\textbf{Initialization:}}
  \State {Let $z_0[0:1] := \left( \vec{y}_0 \right)  $}
  \State {$z_b[0:1], 1 \le b < N_b$ are undefined.}
  \State {Let $\mathcal{l}_{0} := \ln \left[ 
        p \left(\vec{y}_{0} \, \big|  \,
            {\vec{x}}[0:1]\right)  \right]$}
  \For {$m = 1, . . . , M-1$}
    \For {$b = 0, . . . , N_b-1$}
      \If {$z_{b}[0:m]$ is defined}
        \State {Let $\vec{y}_u := z_{b}[m-1] $}
        \State {Let $z_{b, 0}[0:m+1] := z_{b}[0:m] 
                \frown \left\{ \vec{y}_u  \right\}  $} 
            \Comment {A horizontal move $P \rightarrow Q$ in 
            Fig. \ref{fig:path_alignment}}.
        \State {
              $\mathcal{l}_{b,0} := \ln \left[ 
                  p \left(\vec{y}_{u} \big| 
                      z_b[0:m], 
                      \vec{x}[0:m+1], \Theta^{(i)}\right)  \right]
                  + \mathcal{l}_b$}

        \If {$u+1 \le  L - 1$}
          \State {Let $z_{b, 1}[0:m+1] 
          := z_{b}[0:m] \frown \left\{ \vec{y}_{u+1}  \right\}  $} 
              \Comment {A diagonal move $P \rightarrow R$ in Fig. \ref{fig:path_alignment}}.
          \State  {
              $\mathcal{l}_{b,1} := \ln \left[ 
                  p \left(\vec{y}_{u+1} \big| 
                      z_b[0:m], 
                      \vec{x}[0:m+1], \Theta^{(i)}\right)  \right] 
                          + \mathcal{l}_b$}
      \EndIf
      \EndIf
    \EndFor
    \State {Sort a list of items
    $\left\{\mathcal{l}_{b, i}, z_{b, i}[0:m+1] \right\}, \; 0 \le
    b < N_b, i = 0, 1$ 
    with respect to the log likelihood $\mathcal{l}_{b, i}$ 
    in the decreasing order. The top $N_b$ of this sorted list is chosen and re-indexed as 
    follows: 
    $\left\{\mathcal{l}_{b}, z_{b}[0:M] \right\}$, $0 \le b < N_b$}
    where the first item in the sorted list is re-indexed to $b=0$, 
    the second item is re-indexed to $b=1$, and so on.
  \EndFor
  \label{algorithm:n_best_alignment}
  \end{algorithmic}
\end{algorithm}

>>>>

  \Require {A sequence of feature vectors $\vec{x}[0:M]$}
  \Require {A sequence of corresponding labels $\vec{y}_{0:L}$}
  \Require {The beam size $N_b$}
  \Require {The neural network parameter $\Theta^{\left(i\right)}$ 
    for calculating $\vec{z}[u]
    = f^{\left(\Theta^{(i)}\right)}(\vec{x}[0:m+1],\,z[0:u])$} 
    where $m$ is the index of the feature and $u$ is the index of
    time-synchronous label.

  \State {\textbf{Initialization:}}
  \State {Let $z_0[0:1] := \left( \vec{y}_0 \right)  $}
  \State {$z_b[0:1],\, 1 \le b < N_b$ are undefined.}
  \State {Let $\mathcal{l}_{0} := \ln \left[ 
        f^{\left(\Theta^{(i)}\right)}(\vec{x}[0:1],\,z_{<sos>})  \right] $}
  \For {$m = 1, . . . , M-1$}
    \For {$b = 0, . . . , N_b-1$}
      \If {$z_{b}[0:u]$ is defined}
        \State {Let $y_u := z_{b}[u-1] $}
        \State {Let $z_{b, 0}[0:u+1] := z_{b}[0:u] \oplus (y_u)   $} 
            \Comment {A horizontal move $P \rightarrow Q$ in 
            Fig. \ref{fig:path_alignment}}.
        \State {
              $\mathcal{l}_{b,0} := \ln \left[ 
                  f^{\left(\Theta^{(i)}\right)}_{y_u} 
                  \left(\vec{x}[0:m+1],\, z_b[0:u] \right)  \right]
                  + \mathcal{l}_b$}
        \If {$u+1 \le  L - 1$}
          \State {Let $z_{b, 1}[0:u+1] 
          := z_{b}[0:u] \oplus (y_{u+1})  $} 
              \Comment {A diagonal move $P \rightarrow R$ in Fig. \ref{fig:path_alignment}}.
          \State  {
              $\mathcal{l}_{b,1} := \ln \left[ 
                  f^{\left(\Theta^{(i)}\right)}_{y_{u+1}}
                  \left(\vec{x}[0:m+1],\, z_b[0:u]\right)  \right]
                  + \mathcal{l}_b$}
      \EndIf
      \EndIf
    \EndFor
    \State {Sort a list of items
    $\left\{\mathcal{l}_{b, k}, z_{b, k}[0:m+1] \right\}, \; 0 \le
    b < N_b,\, k = 0, 1$ 
    with respect to the log likelihood $\mathcal{l}_{b, k}$ 
    in the decreasing order. The top $N_b$ of this sorted list is chosen and re-indexed as 
    follows: 
    $\left\{\mathcal{l}_{b}, z_{b}[0:M] \right\}$, $0 \le b < N_b$}
    where the first item in the sorted list is re-indexed to $b=0$, 
    the second item is re-indexed to $b=1$, and so on.
  \EndFor
  \label{algorithm:n_best_alignment}
  \end{algorithmic}
\end{algorithm}
